Foundations for statistical inference - Sampling distributions

### 2018-10-15 DATA606/Lab4a/michael-sampling_distributions.Rmd
Additional Work on Lab 4A

6.  When the sample size is larger, what happens to the center?  What about the spread?

@@

-   Take a random sample of size 50 from `price`. Using this sample, what is 
    your best point estimate of the population mean?

-   Since you have access to the population, simulate the sampling 
    distribution for $\bar{x}_{price}$ by taking 5000 samples from the 
    population of size 50 and computing 5000 sample means.  Store these means 
    in a vector called `sample_means50`. Plot the data, then describe the 
    shape of this sampling distribution. Based on this sampling distribution, 
    what would you guess the mean home price of the population to be? Finally, 
    calculate and report the population mean.

-   Change your sample size from 50 to 150, then compute the sampling 
    distribution using the same method as above, and store these means in a 
    new vector called `sample_means150`. Describe the shape of this sampling 
    distribution, and compare it to the sampling distribution for a sample 
    size of 50.  Based on this sampling distribution, what would you guess to 
    be the mean sale price of homes in Ames?

-   Of the sampling distributions from 2 and 3, which has a smaller spread?  If
    we're concerned with making estimates that are more often close to the 
    true value, would we prefer a distribution with a large or small spread?

>>>>

6.  When the sample size is larger, what happens to the center?  **The center becomes closer to the population mean.**  What about the spread? **The spread narrows.**

@@

-   Take a random sample of size 50 from `price`. Using this sample, what is 
    your best point estimate of the population mean?
    ```{r}
    avg_price <- mean(sample(price, 50))
    avg_price
    ```
    **This is the best estimate of the population mean.**

-   Since you have access to the population, simulate the sampling 
    distribution for $\bar{x}_{price}$ by taking 5000 samples from the 
    population of size 50 and computing 5000 sample means.  Store these means 
    in a vector called `sample_means50`. 
    ```{r}
    for(i in 1:5000){
      sample_means50[i] <- mean(sample(price, 50))
    }
    ```
    Plot the data, then describe the shape of this sampling distribution.

    **The distribution is normally distributed.**

    ```{r, echo=FALSE}
    ggplot() + geom_histogram(aes(sample_means50), bins=100) + geom_vline(xintercept=mean(sample_means50), linetype="dashed", color="red")
    ```

    Based on this sampling distribution, what would you guess the mean home price of the population to be? **Roughly $180K.**

    Finally, calculate and report the population mean.
    ```{r}
    mean(price)
    ```

-   Change your sample size from 50 to 150, then compute the sampling 
    distribution using the same method as above, and store these means in a 
    new vector called `sample_means150`. 
    ```{r}
    sample_means150 <- rep(NA, 150)
    for(i in 1:5000){
      sample_means150[i] <- mean(sample(price, 150))
    }
    ```
    Describe the shape of this sampling distribution, and compare it to the 
    sampling distribution for a sample size of 50.  Based on this sampling 
    distribution, what would you guess to be the mean sale price of homes in Ames?
    ```{r}
    df <- data.frame(price=sample_means150, N=c("150"))
    df <- data.frame(price=sample_means50, N=c("50")) %>%
      rbind(df) %>%
      mutate(N = as.factor(N))
    ggplot(df) + geom_density(aes(x=price, fill=N, alpha=0.2)) + guides(alpha="none")
    ```

    **Roughly $180K still but I'm more certain of it.**

-   Of the sampling distributions from 2 and 3, which has a smaller spread?  
    **The one with 150 observations in the sample.**
    If we're concerned with making estimates that are more often close to the 
    true value, would we prefer a distribution with a large or small spread?
    **As large as we can reasonably get.**
